---
title: "assignment2"
author: "poornima_joshi"
date: "9/30/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Documents/R")
```
Libraries 
```{r library packages}
library(mice)
library(MASS)
library(VIM)
library(stats)
library(car)
library(fmsb)
library(e1071)
library(vcd)
library(plyr)
```

Use the smokers data file from the past weeks lecture to develop an ANOVA model. Include the following items and upload an .rmd file:

1.	Review the data and develop a research question and null/alternative hypothesis that can be tested using the information you have. 

The data below list % of smokers based on income and age, develop a model that assesses the influence income and age have on smoking. 

α=0.05
#H0: Income has no significnt effect on smoking
#H0: Age has no significant effect on smoking
#H0: Income and Age interaction has no significant effect on smoking


```{r read csv file}
smoker.data <- data.table(read.csv("smokersdata.csv", header = TRUE))
str(smoker.data)
head(smoker.data)
summary(smoker.data)
countNA(smoker.data)
```
2.	Ensure the variable classes are correct. 

```{r cars}
print(class(dt))
```

3.	Develop an ANOVA object in order to test your hypothesis, run a post-hoc test and interpret the results as it relates to your research question.

#Anova
Response variable : smoking
Factors : Age, Income


```{r Income factor only}
# Choosing Income as a factor first
smoker.data <- data.table(read.csv("smokersdata.csv", header = TRUE))
smoker.data$Income <- as.factor(smoker.data$Income)
str(smoker.data)
smoker.model_1 <- aov(X.Smokers~Income, data = smoker.data)
summary(smoker.model_1)

```
Since the pValue is greater than 0.05, it is not significant. We fail to reject the null hypothesis. Income has no effect on smoking.

```{r Age factor only}
# Choosing Age as a factor first
smoker.data <- data.table(read.csv("smokersdata.csv", header = TRUE))
smoker.data$Age <- as.factor(smoker.data$Income)
str(smoker.data)
smoker.model_2 <- aov(X.Smokers~Age, data = smoker.data)
summary(smoker.model_2)

```
Since the pValue is greater than 0.05, it is not significant. We fail to reject the null hypothesis. Age has no effect on smoking.

4.	If you used only one factor variable in step three include, add the second and re-interpret the results. 

```{r Income and Age factor}
smoker.data <- data.table(read.csv("smokersdata.csv", header = TRUE))
smoker.data$Income <- as.factor(smoker.data$Income)
smoker.data$Age <- as.factor(smoker.data$Age)
str(smoker.data)
smoker.model_3 <- aov(X.Smokers~ Income + Age, data = smoker.data)
TukeyHSD(smoker.model_3)
```

Since the pValue is less than 0.05, it is significant. We reject the null hypothesis. Age and Income interaction has effect on smoking.
Seems like the differences between 3-1 and 3-2 in Age are significant


5.	Create an interaction plot using all the variables then explain if the plot supports your model findings or not. 
```{r Interaction plot}
attach(smoker.data)
interaction.plot(smoker.data$Age,smoker.data$Income,smoker.data$X.Smokers,type="b",col=c(2:3),leg.bty="o",leg.bg="beige",lwd=2,pch=c(18,24),xlab="Age",ylab="Smoking",main="Interaction plot")
```

Age has an effect on smoking irrespective of income level.