
---
title: "Predicting success of an app in Play Store"
author: "Tyler Remick and Poornima Joshi"
date: "11/30/2018"
output: ioslides_presentation
---

---
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Documents/R/android apps")
```

## 1.	Factors that influence success in the App market?

- Rating, Type, Reviews, Category, Last updated and icon  directly influence Installations of an in the app market
- According to studies for every 300 downloads a $1 was generated through ad-monetization

This study matters to:

- App developers
- App market analysts
- Users of mobile apps


## 2.	Gather data for analysis
- Data was extracted from kaggle.
https://www.kaggle.com/lava18/google-play-store-apps
- The kaggle data was extracted by using Selenium and scraping the Google Play store page.


## 2.1 This is how the raw data looked like
```{r import dataset, echo=FALSE}
library("foreign")
raw_data <- read.csv("clean_googleplaystore.csv")
str(raw_data)
```

## 2.2 Peak into the data{.smaller}

```{r, echo=FALSE}
# Correlation plot of Installs v/s ratings
library(ggplot2)
data <- na.omit(raw_data)
g <- ggplot(data, aes(x=Installs, y=Rating)) + geom_point() + geom_smooth(method="lm")
plot(g)
```

## 2.2 Cleaning and preparing data for analysis{.smaller}
  - Convert all app sizes to MB
  - Remove '+' from 'Number of Installs' to make it numeric
  - Dropping unused columns
  - Categorised the number of installs less than 100,000 as unsuccessful and  greater than 100,000 as successful

```{r prepare the dependent variable, include=FALSE}
# Categorised the number of installs less than 100,000 as 0 and  greater than as 1
data$Installs <- ifelse( data$Installs < 100000 , 0, 1)
data$installations <- factor(data$Installs)
#data$out <- relevel(data$installations, ref='10000')
data$Type <- factor(ifelse(data$Type == 'Free', 1, 0))
data = data[,-c(1, 2,7,9,10,11,12, 13, 14)]
str(data)
```


## 3 Classifying apps as successful or not using Logistic regression model{.smaller}
```{r splitting data, include=FALSE}
# Splitting our data into training and test set
set.seed(100)
trainingRows <- sample(1:nrow(data), 0.8*nrow(data))
training <- data[trainingRows, ]
test <- data[-trainingRows, ]
```

```{r regression model, include=FALSE, comment=""}
# Now we’ll execute a logistic regression with independent variables.
default.model <- glm(installations~ . ,family="binomial"(link = "logit"),training)
```

```{r regression model summary, echo=FALSE, comment=""}
summary(default.model)
```
## 4 Predicting on test data to see if the apps are successful or not{.smaller}
```{r , comment=""}
pred.model <- predict.glm(default.model,test,type='response')
head(pred.model)

modelhit <- mean(pred.model!=test$installations)
modelhit
```
```{r}
#Predicting for a value
xx <- data.frame(Category="FAMILY",Reviews=23060,Size=21.000,Type='1',Rating=4.2)
xxpred <- predict(default.model,xx,type='response')
xxpred
#Pretty high chance according to the data we have,what if we cut the reviews to 3000?
xx.11 <- data.frame(Category="FAMILY",Reviews=3000,Size=21,Type='1',Rating=4.2)
xxpred.1 <- predict(default.model,xx.11,type='response')
xxpred.1
#Likelihood drops to 44%
new.data.test <- data.frame(Category="FAMILY",Reviews=3000,Size=21,Type='0',Rating=0)
new.data.test.pred <- predict(default.model,new.data.test, type = "response")
new.data.test.pred
```

## 5 Measuring True Positives and False Positives{.smaller}
```{r, include=FALSE}
library(ROCR)
```
```{r, comment="", echo=FALSE}
#In order to use the package we first have to set the prediction 
newpred <- prediction(pred.model,test$installations)
#Next we want to measure true possitives which is "tpr" and also False Positives "fpr"
newpred.performance <- performance(newpred, measure = "tpr",x.measure = "fpr")
#then we plot these two measures
plot(newpred.performance)
#Looking pretty good, we can also get the AUC again using the performance function
AUC <- performance(newpred, measure = "auc")
AUC
```

## 6 Conclusion
- Installs is a good indicator for sucess of an Android app
- Rating, Review, Type and Categories are factors that influence the success of an app


<style>
slides > slide { overflow: scroll; }
slides > slide:not(.nobackground):after {
content: '';
}
</style>