
---
title: "Predicting success of an app"
author: "Tyler Remick and Poornima Joshi"
date: "11/30/2018"
output: ioslides_presentation
---

---
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Documents/R/android apps")
```

## 1.	Factors that influence success in the App market?
Ad-monetization which seems to generate $ 1 for every 300 downloads.
Rating, Type, Reviews, Category, Last updated and icon  directly influence Installations of an in the app market

This study matters to:
- App developers
- App market analysts
- Users of mobile apps


## 2.	Gather data for analysis
- Data was extracted from kaggle.
https://www.kaggle.com/lava18/google-play-store-apps
- The kaggle data was extracted by using Selenium and scraping the Google Play store page.


### 2.1 This is how the raw data looked like
```{r import dataset, include=FALSE}
library("foreign")
raw_data <- read.csv("clean_googleplaystore.csv")
raw_data <- na.omit(raw_data)
```
***
```{r rawdata}
str(raw_data)
```
*** 
### 2.2 Peak into the data{.smaller}

```{r histogram, fig.cap="Histogram of Rating", echo=FALSE}
hist(raw_data$Rating)
```
***
### 2.2 Peak into the data
```{r plots, fig.align='left', fig.cap="Number of installations"}
barplot(prop.table(table(raw_data$Installs)))
```
***
```{r}
library(ggplot2)
g <- ggplot(raw_data, aes(x=Installs, y=Rating)) + geom_point() + geom_smooth(method="lm")
plot(g)
```

## 2.2 Cleaning and preparing data for analysis{.smaller}
  - Convert all app sizes to MB
  - Remove '+' from 'Number of Installs' to make it numeric
  - Reordering Installs
  - Convert all the installs to factor levels and releveling it to reference level '1'
  - Dropping unused columns

```{r prepare the dependent variable, include=FALSE}
data <- raw_data
data$Installs <- ifelse( data$Installs < 100000 & data$Installs < 500000000, 0, 1)
data$installations <- factor(data$Installs)
#data$out <- relevel(data$installations, ref='10000')
data$Type <- factor(ifelse(data$Type == 'Free', 1, 0))
data = data[,-c(1, 2,7,9,10,11,12, 13, 14)]
str(data)
```


## 3 Logistic regression model{.smaller}
Get atleast 100,000 installations of a given app.
```{r splitting data, include=FALSE}
table(data$installations)
set.seed(100)
trainingRows <- sample(1:nrow(data), 0.8*nrow(data))
training <- data[trainingRows, ]
test <- data[-trainingRows, ]
```


```{r regression model, include=FALSE, comment=""}
# Now we’ll execute a logistic regression with independent variables.
default.model <- glm(installations~ . ,family="binomial"(link = "logit"),training)
```

```{r regression model summary, echo=FALSE, comment=""}
summary(default.model)
```
## 4 Predicting on test data{.smaller}
```{r , comment=""}
pred.model2 <- predict.glm(default.model,test,type='response')
head(pred.model2)

#pred.model2.1 <- ifelse(pred.model2 > 0.5,1,0)
#head(pred.model2.1)
model3hit <- mean(pred.model2!=test$installations)
model3hit
```


## 5 Measure true possitives and False Positives{.smaller}
```{r, include=FALSE}
library(ROCR)
```
```{r, comment="", echo=FALSE}
#In order to use the package we first have to set the prediction 
newpred <- prediction(pred.model2,test$installations)
#Next we want to measure true possitives which is "tpr" and also False Positives "fpr"
newpred.performance <- performance(newpred, measure = "tpr",x.measure = "fpr")
#then we plot these two measures
plot(newpred.performance)
#Looking pretty good, we can also get the AUC again using the performance function
AUC <- performance(newpred, measure = "auc")
AUC
```
```